---
title: "IRT facet"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F, message=F)
```


```{r, include=F, eval=T}
library(here)
source(here("tools/functions.R"))
library(flextable)
library(tidyverse)
library(knitr)
load(here::here("IRT table.Rdata"))
```

# Annex 2.

## IRT information per facet


Note: *b1* to *b4* columns represents the difficulty parameters, *a* stands for the discrimination parameter. Values in the *DIF* column represent McFaden's pseudo R squared values. They are only printed if the Chi^2 test is significant. The *DIF.3* column represents DIF values without excluding the middle-age category, that is, using three different groups for DIF analyses.


```{r, results="asis", eval=T}

IRT.table <- y[,-9]
load(here::here("IRT table with 3 groups.Rdata"))
IRT.table$DIF.3 <- y$DIF

regulartable(IRT.table) %>% 
  autofit()  %>% 
  width(j = ~ label, width = 3.4) %>% 
  width(j = ~ item, width = 1) %>% 
  width(j = ~ b1+b2+b3+b4+a, width = 0.5) %>% 
  width(j = ~ DIF, width = 0.6)%>% 
  width(j = ~ DIF.3, width = 0.6)
```

